Operator evolution from the similarity renormalization group and the Magnus expansion

### 2019-09-25 Notes/Operator_evolution/operator_evolution.tex
Updated operator evolution draft
Minor addition.
Updated operator evolution notes
Changing the order of things in the introduction.

@@

-- Implementation to many-body calculations and SRG decoupling.

@@

\noindent{%
-- SRG operator evolution for different potentials and generators.
}
\\
-- General questions to address: universality for operators, different generators.
\\
-- Momentum projection operator.
%
\begin{itemize}
	\item Contours and general behavior: SRG transformation shifts strength of operator to low-momentum.
	\item Deuteron momentum distributions. Why does this make sense with the transformed operators?
	\item Diagonals and far off-diagonals. Universality.
	\item Same questions but with figures of the integrand.
\end{itemize}
%
-- $\hat{r}^2$ operator.

>>>>

\textbf{NN interaction and SRG decoupling.}

@@

@@

\noindent{%
-- SRG operator evolution for different potentials and generators.
}
\\
-- General questions to address: universality for operators, different generators.
\\
-- Momentum projection operator.
%
\begin{itemize}
	\item Contours and general behavior: SRG transformation shifts strength of operator to low-momentum.
	\item Deuteron momentum distributions. Why does this make sense with the transformed operators?
	\item Diagonals and far off-diagonals. Universality.
	\item Same questions but with figures of the integrand.
\end{itemize}
%
-- Note, the unitary transformations and evolved wave functions for different potentials are not the same (at low momentum too) swhich implies that evolved operators cannot have the same universality property as the evolved potentials since they are dependent on the evolved wave functions.
\\
-- $\hat{r}^2$ operator.
